Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 supplement.tex
putting DSL 's in supplement

\begin{center}
\begin{tabular}{|l|l|}
  \hline Input&Output\\
  \hline\multicolumn{2}{|c|}{Double}\\
  \hline
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB \\
  \hline\multicolumn{2}{|c|}{Extract string delimited by ',' (inclusive),' '}\\
  \hline
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to input delimited by '.'}\\
  \hline
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to string delimited by ' ','.'}\\
  \hline
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN \\
%  \hline\multicolumn{2}{|c|}{Apply double to input delimited by '.'}\\
%  \hline
%FWhb.jYMdi & FWhbFWhbjYMdijYMdi \\
% JZB.WEwgH & JZBJZBWEwgHWEwgH \\
% SgA.Kxo.RyF & SgASgAKxoKxoRyFRyF \\
% NMApj.OaPBs.uZm.iCZy & NMApjNMApjOaPBsOaPBsuZmuZmiCZyiCZy \\
  \hline\multicolumn{2}{|c|}{Apply strip to string delimited by ',','.'}\\
  \hline
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE \\
  \hline\multicolumn{2}{|c|}{Drop first character}\\
  \hline
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{|l|l|}
  \hline Input&Output\\
  \hline\multicolumn{2}{|c|}{Double}\\
  \hline
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB \\
  \hline\multicolumn{2}{|c|}{Extract string delimited by ',' (inclusive),' '}\\
  \hline
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to input delimited by '.'}\\
  \hline
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to string delimited by ' ','.'}\\
  \hline
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN \\
  \hline\multicolumn{2}{|c|}{Apply strip to string delimited by ',','.'}\\
  \hline
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE \\
  \hline\multicolumn{2}{|c|}{Drop first character}\\
  \hline
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT \\
\hline
\end{tabular}
\end{center}

\section{Learned DSLs}

Here we present representative DSLs learned by
our model. DSL primitives discovered by the algorithm are prefixed with \code{#}.
Variables are prefixed with \$, and we use De Bruijn indices to model variables~\cite{pierce}.
We abbreviate lambda as \textbackslash.

\pagebreak
\onecolumn
\subsection{Boolean circuits}

\begin{verbatim}
#(\ (\ (\ (nand (nand $0 $1) (nand $2 (nand $0 $2))))))
#(\ (\ (nand (nand $0 $1) (nand $0 $1))))
#(\ (\ (nand (nand $0 $0) (nand $1 $1))))
#(\ (\ (\ (\ (nand (nand $0 $1) (nand $2 $3))))))
#(\ (\ (\ (nand (nand $0 $0) (nand $1 (nand $2 $1))))))
#(\ (\ (#(\ (\ (nand (nand $0 $1) (nand $0 $1)))) $0 (nand $1 $0))))
#(\ (\ (\ (nand (nand $0 $1) (nand $0 (nand $2 $0))))))
#(\ (\ (#(\ (\ (\ (nand (nand $0 $1) (nand $0 (nand $2 $0)))))) $0 $1 (nand $1 $1))))
#(\ (\ (nand $0 (nand $1 $0))))
#(\ (#(\ (\ (\ (nand (nand $0 $1) (nand $2 (nand $0 $2)))))) (nand $0 $0)))
#(\ (\ (\ (\ (nand (nand $0 $1) (nand $2 (nand $3 $2)))))))
\end{verbatim}

\subsection{Symbolic regression}
\begin{verbatim}
#(\ (* (+ REAL $0) REAL))
#(\ (#(\ (+ $0 REAL)) (#(\ (* $0 (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0)))) $0)))
#(\ (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0)))
#(\ (#(\ (#(\ (+ $0 REAL)) (#(\ (* (#(\ (#(\ (+ $0 REAL)) (#(\ (* $0 (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0)))) $0))) $0) $0)) $0))) (+ $0 $0)))
#(\ (#(\ (+ $0 REAL)) (#(\ (* (#(\ (#(\ (+ $0 REAL)) (#(\ (* $0 (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0)))) $0))) $0) $0)) $0)))
#(\ (* (#(\ (+ $0 REAL)) $0) (#(\ (+ (* $0 (* $0 REAL)) REAL)) $0)))
#(\ (+ (* $0 (* $0 REAL)) REAL))
#(* REAL)
#(\ (* (#(\ (#(\ (+ $0 REAL)) (#(\ (* $0 (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0)))) $0))) $0) $0))
#(\ (* $0 (#(\ (+ (* $0 (* $0 REAL)) REAL)) (#(\ (+ $0 REAL)) $0))))
#(\ (+ $0 REAL))
\end{verbatim}

\subsection{String editing}
\begin{verbatim}
#(\ (\ (#(nth (incr 0)) (split $0 (#(\ (\ (join (chr->str $0) (map (\ (caseCapitalize $0)) $1)))) $1 $0)))))
#(\ (\ (join (chr->str $0) (map (\ (strip $0)) $1))))
#(\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (++ $0 $0))))
#(\ (#(join empty) (split '.' $0)))
#(#(\ (\ (\ (#(\ (\ (slice $0 (len $1) $1))) (nth $0 $1) (decr $2))))) (decr 0))
#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (slice $2 (incr $2) $0)))))
#(#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (#(\ (\ (slice $0 (len $1) $1))) $0 $2))))) (incr 0))
#(\ (\ (\ (#(\ (\ (slice $0 (len $1) $1))) (nth $0 $1) (decr $2)))))
#(\ (\ (strip (nth 0 (split $0 (#(nth (incr 0)) $1))))))
#(\ (#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (#(\ (\ (slice $0 (len $1) $1))) $0 $2))))) (decr $0)))
#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (#(\ (slice $0 (incr (incr $0)))) $2 $0)))))
#(\ (\ (slice $0 (incr $0) (nth (incr $0) $1))))
#(\ (\ (#(\ (\ (slice $0 (len $1) $1))) (#(\ (\ (strip (nth 0 (split $0 (#(nth (incr 0)) $1)))))) $0 $1) (incr 0))))
#(\ (\ (caseUpper (#(nth (incr 0)) (split $0 (#(\ (\ (join (chr->str $0) (map (\ (caseCapitalize $0)) $1)))) $1 $0))))))
#(\ (\ (#(\ (\ (++ (chr->str $0) (#(nth (incr 0)) $1)))) (split $0 (nth 0 $1)) $0)))
#(\ (#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (#(\ (\ (slice $0 (len $1) $1))) $0 $2))))) (decr (decr $0))))
#(\ (\ (join (chr->str $0) (map (\ (caseCapitalize $0)) $1))))
#(\ (\ (#(\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (++ $0 $0)))) (split '.' (#(\ (\ (strip (nth 0 (split $0 (#(nth (incr 0)) $1)))))) $0 $1)) '.')))
#(\ (\ (\ (#(\ (\ (++ (chr->str $0) (#(nth (incr 0)) $1)))) (split $0 (#(\ (\ (\ (++ (nth $0 (split $1 $2)) (chr->str $1))))) $1 $2 0)) $0))))
#(\ (\ (slice $0 (incr (incr $0)) (#(nth (incr 0)) $1))))
#(join empty)
#(\ (\ (\ (++ (nth $0 (split $1 $2)) (chr->str $1)))))
#(\ (\ (nth 0 (split $0 (#(nth (incr 0)) $1)))))
#(\ (slice $0 (incr (incr $0))))
#(nth (incr 0))
#(\ (join empty (map (\ (caseCapitalize $0)) $0)))
#(\ (\ (#(\ (\ (\ (join (chr->str $0) (map $1 $2))))) $0 (\ (#(\ (\ (slice $0 (len $1) $1))) $0 $2)))))
#(\ (\ (slice $0 (len $1) $1)))
#(\ (\ (\ (join (chr->str $0) (map $1 $2)))))
#(\ (\ (++ (chr->str $0) (#(nth (incr 0)) $1))))
\end{verbatim}

\subsection{List functions}
